Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-21 doc/asplos13/evaluation.tex
change uses of "todo" --> "TODO"
pass on section 3
a few notes on evaluation; adding plots soon

\section{Evaluation} \label{sec:evaluation}
%todo put method in here, if it stays small

@@

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees and a geometric 1.6B-vertex tree
\footnote{T3L: -t 0 -b 2000 -q 0.200014 -m 5 -r 7\\
          T2L: -t 1 -a 2 -d 23 -b 7 -r 220\\
          T1L: -t 1 -a 3 -d 13 -b 4 -r 29\\
          T1XL: -t 1 -a 3 -d 15 -b 4 -r 29\\}.
Both systems do relatively poorly on the binomial tree because it is very deep and a
traversal produces little parallelism, which both systems depend on.
\todo{data from our trace would be nice here}. Figure~\ref{fig:grappa-xmt-uts}
shows the performance in terms of number of vertices visited per
second versus number of compute nodes. The Grappa results are for the
best parameter values from a limited search over \flushtimeout~and
\asyncforthr~\TODO{want to say this in general at beginning of eval?}.
Grappa with 16 machines is faster than the entire XMT. Grappa achieves
\checkme{112Mvert/s} with \checkme{60 machines} and the
XMT achieves only 50Mvert/s. Scaling up, Grappa adds 2Mvert/s/nodes
and the XMT adds 850Kvert/s/node. Grappa's scaling slows down at
\checkme{90} machines because of the unscalability of our aggregation
mechanism as there are more network endpoints.

Grappa
\TODO{Preston/Simon: why the xmt stops scaling, readfe retries?}

@@

>>>>

\section{Evaluation} \label{sec:evaluation}

@@

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees and a geometric 1.6B-vertex tree
\footnote{T3L: -t 0 -b 2000 -q 0.200014 -m 5 -r 7\\
          T2L: -t 1 -a 2 -d 23 -b 7 -r 220\\
          T1L: -t 1 -a 3 -d 13 -b 4 -r 29\\
          T1XL: -t 1 -a 3 -d 15 -b 4 -r 29\\}.
Both systems do relatively poorly on the binomial tree because it is very deep and a
traversal produces little parallelism, which both systems depend on.
\TODO{data from our trace would be nice here}. Figure~\ref{fig:grappa-xmt-uts}
shows the performance in terms of number of vertices visited per
second versus number of compute nodes. The Grappa results are for the
best parameter values from a limited search over \flushtimeout~and
\asyncforthr~\TODO{want to say this in general at beginning of eval?}.
Grappa with 16 machines is faster than the entire XMT. Grappa achieves
\checkme{112Mvert/s} with \checkme{60 machines} and the
XMT achieves only 50Mvert/s. Scaling up, Grappa adds 2Mvert/s/nodes
and the XMT adds 850Kvert/s/node. Grappa's scaling slows down at
\checkme{90} machines because of the unscalability of our aggregation
mechanism as there are more network endpoints.

@@

\subsection{Sensitivity}

\subsection{Latency tolerance parameters}

\paragraph{Benefit of aggregator}
what happens with aggregator on and off

\paragraph{Latency}
aggregation latency and delegate latency

\paragraph{Number of workers}
We need enough workers to cover the network+aggregation latency, but more just slow things down.

UTS
BFS

\subsubsection{Work stealing parameters}

\paragraph{Chunk size}

it's important to steal multiple tasks to 
amortize cost of stealing
spread work out quickly in large system

there are times when it's useful to steal lots of stuff, even though
we steal only a few things most of the time.

UTS

\paragraph{Parallel loop threshold}

allows us to amoritize task creation overhead and exploit locality
Gets us a 2x bump in performance
not too sensitive

UTS
BFS
